%! Author = cspiller
%! Date = 16/11/2022

\GlsXtrEnableInitialTagging{abbreviation}{\itag}

\newabbreviation{sie}{SIE}{\itag{S}ony \itag{I}nteractive \itag{E}ntertainment}
\newabbreviation{paas}{PaaS}{\itag{P}latform \itag{a}s \itag{a} \itag{S}ervice}
\newabbreviation{aws}{AWS}{\itag{A}mazon \itag{W}eb \itag{S}ervices}
\newabbreviation{hrtf}{HRTF}{\itag{h}ead-\itag{r}elated \itag{t}ransfer \itag{f}unction}
\newabbreviation{api}{API}{\itag{a}pplication \itag{p}rogramming \itag{i}nterface}
\newabbreviation{ps5}{PS5}{\itag{P}lay\itag{S}tation \itag{5}}
\newabbreviation{dsp}{DSP}{\itag{d}igital \itag{s}ignal \itag{p}rocessing}
\newabbreviation{ux}{UX}{\itag{u}ser \itag e{x}perience}
\newabbreviation{mvp}{MVP}{\itag{m}inimum \itag {v}iable \itag {p}roduct}
\newabbreviation{poc}{POC}{\itag{p}roof \itag {o}f \itag {c}oncept}
\newabbreviation{ec2}{EC2}{Amazon \itag{E}lastic \itag {C}ompute \itag {C}loud}
\newabbreviation{s3}{S3}{Amazon \itag{S}imple \itag {S}torage \itag {S}olution}
\newabbreviation{sla}{SLA}{\itag{s}ervice-\itag{l}evel \itag{a}greement}
\newabbreviation{ci}{CI}{\itag{C}ontinuous \itag{I}ntegration}
\newabbreviation{gdpr}{GDPR}{\itag{G}eneral \itag{D}ata \itag{P}rotection \itag{R}egulation}
\newabbreviation{ide}{IDE}{\itag{I}ntegrated \itag{D}evelopment \itag{E}nvironment}
\newabbreviation{cicd}{CI/CD}{\itag{C}ontinuous \itag{I}ntegration/\itag{C}ontinuous \itag{D}eployment}
\newabbreviation{dom}{DOM}{\itag{D}ocument \itag{O}bject \itag{M}odel}
\newabbreviation{sdk}{SDK}{\itag{S}oftware \itag{D}evelopment \itag{K}it}
\newabbreviation{ip}{IP}{\itag{I}ntellectual \itag{P}roperty}
\newabbreviation{ui}{UI}{\itag{U}ser \itag{I}nterface}
\newabbreviation{mui}{MUI}{\itag{M}aterial \itag{U}ser \itag{I}nterface}

\newglossaryentry{tempest_3d_audio}{name={Tempest 3D Audio Engine}, description={The proprietary audio engine used by the PlayStation 5 in order to render ambisonic audio files to headphones.}}
\newglossaryentry{pspartner}{name={PlayStation Partner}, description={The name given to any video game developer or retailer who engages with the PlayStation ecosystem in order to sell or develop their products.}, text={Partner}}
\newglossaryentry{spatial_audio}{name={spatial audio}, description={Is the manipulation of sound produced by stereo speakers to mimic the human localization of sound sources in three-dimensional space.}}
\newglossaryentry{devnet}{name={DevNet}, description={A private web resource accessible only to licensed PlayStation developer, publisher and middleware companies. On this site you are able to access PlayStation API documents and order PlayStation development kits.}}
\newglossaryentry{react}{name={React.js}, description={A free and open-source Javascript library, maintained by Meta, that is used primarily for developing front-end user interfaces by rendering components to the DOM in web browsers.}}
\newglossaryentry{nodejs}{name={Node.js}, description={A free and open-source server environment that allows the execution of JavaScript code outside of a web browser. In this project it was used to build the front-end web interface.}}
\newglossaryentry{aws-lambda}{name={AWS Lambda}, description={Part of Amazon's serverless computing services, these Lambda functions allow a software developer to host and run individual fragments of code that are triggered in response to events. The feature manages the resources required for these pieces of code to run.}}
\newglossaryentry{aws-step-function}{name={AWS Step Function}, description={A service that allows a software developer to orchestrate and schedule serverless workflow pipelines through the use of state machines and tasks. Through this service, a developer is able to easily control the use and order of other AWS services.}}
\newglossaryentry{aws-eventbridge}{name={AWS Eventbridge}, description={A cloud service that allows the communication between disparate AWS serverless components through the use of events.}}
\newglossaryentry{aws-api-gateway}{name={AWS API Gateway}, description={An AWS service that allows developers to create and deploy their own custom APIs that allow access to data and application logic.}}
\newglossaryentry{aws-ecr}{name={AWS Elastic Container Registry}, description={An AWS function that allows the user to host and deploy container images.}}
\newglossaryentry{container-image}{name={container image}, description={A standalone package of sotware that contains everything needed in order to run an application. This allows for the identical deployment and running of applications independant of the underlying infrastructure.}}
\newglossaryentry{docker}{name={Docker}, description={A set of products that allows developers to virtually deploy operating systems and software packages in reuseable containers. Docker is one of the most widely used prodcuts for this purpose.}}
\newglossaryentry{aws-sqs}{name={AWS Simple Queue Service}, description={A message queue service from AWS that allows the sending and receiving of messages without data loss.}}
\newglossaryentry{agile}{name={Agile}, description={A framework or a collection of methods through which software projects can be conducted. Defined by its focus on incremental and iterative development practices.}}
\newglossaryentry{gdk}{name={game development kit}, description={Game development kits are use to develop software that is intended to run on a specific game console. They provide the hardware and software needed in order to do this.}}
\newglossaryentry{states-language}{name={Amazon States Language}, description={A JSON-based, structured language that is used to define a state machine workflow in AWS. Used primarily to orchestrate other services within AWS.}}
\newglossaryentry{amplify}{name={AWS Amplify}, description={An AWS product that hosts web applications. Integrating with code repositories, it supports the use of~\gls{cicd}}}
\newglossaryentry{threejs}{name={three.js}, description={A JavaScript library that can be used to build and render 3D content in a web browser.}}

